On the link between functional traits and growth rate: meta-analysis shows effects change with plant size, as predicted

### 2016-01-19 MS.tex
Minor edits for the abstract Update word count of abstract

\begin{document}
\mstitlepage
\noindent
\parindent=1.5em
\addtolength{\parskip}{.3em}
\doublespacing
\linenumbers
\section{Summary 268/350}\label{abstract}
\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\itemsep1pt\parskip0pt\parsep0pt
\item A plant's growth rate is seen as a central element of its ecological strategy, and as determined by its traits. Yet the literature is inconsistent about the empirical correlation between functional traits and growth, casting doubt on the capacity of some prominent traits to influence growth rate.

\item We propose that traits should influence growth in a way that depends on the size of individual plants. We outline mechanisms and hypotheses based on new theory, and test these predictions in tree species using a meta-analysis of 103 studies ($>$ 500 correlations) for five traits (specific leaf area, wood density, maximum height, seed mass and maximum assimilation rate). To capture the effects of size, we tested for a shift in the direction of correlation between growth rates and traits across three plant stages: seedling, sapling and adult.

\item Results were consistent with predictions. Specific leaf area was correlated with relative growth rate (RGR) in seedlings but not in adult plants. Correlations of RGR with wood density and assimilation rate were not affected by stage. Seed mass and maximum height were correlated with RGR only in one plant stage category: seedlings and adults, respectively. Despite a sizeable literature on traits and growth, coverage was still limited for wood density, seed mass, maximum height and assimilation rate. There is still scope for strengthening our understanding of correlations between traits and growth through adding further empirical studies for traits and size-classes underrepresented in the literature.

>>>>

\begin{document}
\mstitlepage
\noindent
\parindent=1.5em
\addtolength{\parskip}{.3em}
\doublespacing
\linenumbers
\section{Summary 288/350}\label{abstract}
\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\itemsep1pt\parskip0pt\parsep0pt
\item A plant's growth rate is seen as a central element of its ecological strategy, and as determined by its traits. Yet the literature is inconsistent about the empirical correlation between functional traits and growth, casting doubt on the capacity of some prominent traits to influence growth rate.

\item We propose that traits should influence growth in a way that depends on the size of individual plants. We outline mechanisms and hypotheses based on new theory, and test these predictions in tree species using a meta-analysis of 103 studies ($>$ 500 correlations) for five traits (specific leaf area, wood density, maximum height, seed mass and maximum assimilation rate). To capture the effects of plant size, we tested for a shift in the direction of correlation between growth rates and traits across three ontogenic stages: seedling, sapling and adult.

\item Results were consistent with predictions, despite some limitations arising from unequal number of observations across stages. Specific leaf area was correlated with relative growth rate (RGR) in seedlings but not in adult plants. Correlations of growth with wood density and assimilation rate were not affected by stage. Seed mass and maximum height were correlated with RGR only in one plant stage category: seedlings and adults, respectively. Despite a sizeable literature on traits and growth, coverage was still limited for 4 of the 5 traits. Clearly, there is scope for strengthening our understanding on the link between traits and growth through adding further empirical studies for traits and size-classes underrepresented in the literature.
